% prelude.tex
%   - titlepage
%   - dedication
%   - acknowledgments
%   - table of contents, list of tables and list of figures
%   - nomenclature
%   - abstract
%============================================================================


\clearpage\pagenumbering{roman}  % This makes the page numbers Roman (i, ii, etc)



% TITLE PAGE
%   - define \title{} \author{} \date{}
\advisorname{Soumya Ray}
\advisortitle{Professor}
\title{A Decision Theoretic Approach to Natural Language Generation}
\author{NATHAN MCKINLEY}
\date{2013}
%   - The default degree is ``Doctor of Philosophy''
%     (unless the document style msthesis is specified
%      and then the default degree is ``Master of Science'')
%     Degree can be changed using the command \degree{}
\degree{Master of Science}
%   - The default is dissertation, unless the document style
%     msthesis was specified in which case it becomes thesis.
%     If msthesis is specified for the MS margins, you can
%     still have a dissertation if you specify \disseration
%\disseration
%   - for a masters project report, specify \project
%\project
%   - for a preliminary report, specify \prelim
%\prelim
%   - for a masters thesis, specify \thesis
\thesis
%   - The default department is ``Electrical Engineering''
%     The department can be changed using the command \department{}
\department{Electrical Engineering and Computer Science}
%   - once the above are defined, use \maketitle to generate the titlepage
\makeatletter
\renewcommand\@date{January, 2014}
\makeatother
\maketitle

\clearpage
\begin{center}
{\bf CASE WESTERN RESERVE UNIVERSITY
SCHOOL OF GRADUATE STUDIES}\\

We hereby approve the thesis of\\
NATHAN MCKINLEY\\
candidate for the Master of Science degree*.\\
\end{center}
\noindent
Dr. Soumya Ray\\
Dr. Michael Lewicki\\
Dr. Gregory Lee\\
Dr. Vincenzo Liberatore\\

\noindent
Date: December 2, 2013\\

\noindent
*We also certify that written approval has been obtained for any
proprietary material contained therein.

% COPYRIGHT PAGE
%   - To include a copyright page use \copyrightpage
\copyrightpage

% ACKNOWLEDGMENTS
\begin{acknowledgments}
I thank my advisor, Professor Soumya Ray, for his assistance through the entire process of
developing this idea and creating this thesis.  When I began this program I knew very
little of the process of research, but Professor Ray guided me through creating my first
prototype of this system and my first paper for submission to a conference.  From there,
we ended up here, with the submission of my thesis in order to obtain the degree of
Master of Science.  I am very thankful to him for all his help, edits, and guidance.
\end{acknowledgments}

% CONTENTS, TABLES, FIGURES
\tableofcontents
\listoffigures

% ABSTRACT
\begin{umiabstract}
  \input{abstract}
\end{umiabstract}


\clearpage\pagenumbering{arabic} % This makes the page numbers Arabic (1, 2, etc)
